---
title: "NBA Stats (May 2022)"
output: html_notebook
---

Inspired from the course R Programming A-ZT: R For Data Science With Real Exercises! by Kirill Eremenko

Data updated by Sam Roeslin on 9 May 2022

# Top 10 paid players in the NBA (May 2022)
```{r}
Players
```

# Games
```{r}
Games
```

## Number of games for the 3 highest paid players for the 5 last years
```{r}
Games[1:3,5:9]
```

## Number of games for the #1 and #10 highest paid players
```{r}
Games[c(1,10),]
```

# FieldGoals
```{r}
par(mar=c(3.1, 4.1, 2.1, 9.1), xpd=TRUE) #change margins (bottom, left, top, and right)
matplot(t(FieldGoals), type="b", pch=15:18, col=c(1:4,6))
op <- par(cex = 0.7) # change fontsize
legend("right", inset = c(-0.35, 0), legend = Players, pch=15:18, col=c(1:4,6), horiz=F)
```


# Accuracy of each player

FG_per <- FieldGoals/FieldGoalAttempts

```{r}
round(FG_per,3)
```

```{r}
par(mar=c(3.1, 4.1, 2.1, 9.1), xpd=TRUE) #change margins (bottom, left, top, and right)
matplot(t(FG_per), type="b", pch=15:18, col=c(1:4,6))
op <- par(cex = 0.7) # change fontsize
legend("right", inset = c(-0.35, 0), legend = Players, pch=15:18, col=c(1:4,6), horiz=F)
```

# Playtime

# Average minute played per game
```{r}
par(mar=c(3.1, 4.1, 2.1, 9.1), xpd=TRUE) #change margins (bottom, left, top, and right)
matplot(t(MinutesPlayed), type="b", pch=15:18, col=c(1:4,6))
op <- par(cex = 0.7) # change fontsize
legend("right", inset = c(-0.35, 0), legend = Players, pch=15:18, col=c(1:4,6), horiz=F)
```

## Total playtime
PlayTime <- Games*MinutesPlayed

Plot for the top 5 players
```{r}
par(mar=c(3.1, 4.1, 2.1, 9.1), xpd=TRUE) #change margins (bottom, left, top, and right)
matplot(t(PlayTime[1:5,]), type="b", pch=15:18, col=c(1:4,6))
op <- par(cex = 0.7) # change fontsize
legend("right", inset = c(-0.35, 0), legend = Players[1:5], pch=15:18, col=c(1:4,6), horiz=F)
```

# Salary (adjusted for inflation - May 2022)
```{r}
Salary
```

# Evolution of the salary
```{r}
par(mar=c(3.1, 4.1, 2.1, 9.1), xpd=TRUE) #change margins (bottom, left, top, and right)
matplot(t(Salary), type="b", pch=15:18, col=c(1:4,6))
op <- par(cex = 0.7) # change fontsize
legend("right", inset = c(-0.35, 0), legend = Players, pch=15:18, col=c(1:4,6), horiz=F)
```

# Evolution of the salary for #1 and #10 player
```{r}
par(mar=c(3.1, 4.1, 2.1, 9.1), xpd=TRUE) #change margins (bottom, left, top, and right)
matplot(t(Salary[c(1,10),,drop=F]), type="b", pch=15:18, col=c(1:4,6))
op <- par(cex = 0.7) # change fontsize
legend("right", inset = c(-0.35, 0), legend = Players[c(1,10)], pch=15:18, col=c(1:4,6), horiz=F)
```

## Salary by minute played
Salary_per_min <- Salary/PlayTime

```{r}
Salary_per_min
```

```{r}
par(mar=c(3.1, 4.1, 2.1, 9.1), xpd=TRUE) #change margins (bottom, left, top, and right)
matplot(t(Salary_per_min), type="b", pch=15:18, col=c(1:4,6))
op <- par(cex = 0.7) # change fontsize
legend("right", inset = c(-0.35, 0), legend = Players, pch=15:18, col=c(1:4,6), horiz=F)
```



<!-- Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*. -->

<!-- When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file).  -->

<!-- The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed. -->

