---
title: "NBA Stats (May 2022)"
output: html_notebook
---

Inspired from the course R Programming A-ZT: R For Data Science With Real Exercises! by Kirill Eremenko

Data updated by Sam Roeslin on 9 May 2022

# Top 10 paid players in the NBA (May 2022)
```{r}
Players
```

# Games
```{r}
Games
```

## Number of games for the 3 highest paid players for the 5 last years
```{r}
Games[1:3,5:9]
```

## Number of games for the #1 and #10 highest paid players
```{r}
Games[c(1,10),]
```

#Create a function for plotting
myplot <- function(data, rows=1:10){
  Data <-data[rows,,drop=F]
  par(mar=c(3.1, 4.1, 2.1, 9.1), xpd=TRUE) #change margins (bottom, left, top, and right)
  matplot(t(Data), type="b", pch=15:18, col=c(1:4,6))
  op <- par(cex = 0.7) # change fontsize
  legend("right", inset = c(-0.35, 0), legend = Players[rows], pch=15:18, col=c(1:4,6), horiz=F)
}

# FieldGoals
```{r}
myplot(FieldGoals)
```


# Accuracy of each player

FG_per <- FieldGoals/FieldGoalAttempts

```{r}
round(FG_per,3)
```

```{r}
myplot(FG_per)
```

# Playtime

# Average minute played per game
```{r}
myplot(MinutesPlayed)
```

## Total playtime
PlayTime <- Games*MinutesPlayed

Plot for the top 5 players
```{r}
myplot(PlayTime, 1:5)
```

# Salary (adjusted for inflation - May 2022)
```{r}
Salary
```

# Evolution of the salary
```{r}
myplot(Salary)
```

# Evolution of the salary for #1 and #10 player
```{r}
myplot(Salary, c(1,10))
```

## Salary by minute played
Salary_per_min <- Salary/PlayTime

```{r}
Salary_per_min
```

```{r}
myplot(Salary_per_min)
```


<!-- Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*. -->

<!-- When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file).  -->

<!-- The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed. -->

